Estimated Annual Size of Claims Arising from Fire

### 2023-06-01 report/PAPER.tex
it must be finished

% 此处填写摘要内容
\begin{abstract}
    The aim of this study is to construct a mathematical model based on Markov chains to predict \
    the total size of claims paid by insurers in the UK (and specifically England) due to fires in \
    the coming year. We split the regions of England into\ 
    \emph{"South West", "South East", "London", "East of England", "East Midlands", "Yorkshire and The Humber", "North West", "West Midlands", "North East"} \ 
    in order to obtain more refined predictions. First, we used house price data as a proxy for the \
    size of the claim per fire, assuming a fixed ratio of damage to the size of the claim per fire. \
    We then fitted the house price data with a log-normal distribution to obtain the distribution of \
    each claim size. Next, we modelled the number of fires using a Poisson distribution with a high \
    probability estimate. Finally, we use Monte Carlo simulations to estimate the size of the annual \
    fire loss. Our model takes into account two key factors, the number of fires and the size of claims \
    per fire, and provides insurers with an effective tool for predicting and managing fire insurance risk. \
    However, there are some assumptions and limitations to our model, such as our assumption of a fixed ratio \
    of losses to claim sizes per fire, which may not be entirely accurate in real life situations. \
    Future research could further improve this model to increase its predictive accuracy and usefulness. \\
    All data is taken from GOV.UK, the official website of the UK government.\\
    All Source code you can found in my \href{https://github.com/JavaZeroo/markov\_project}{Github: https://github.com/JavaZeroo/markov\_project}

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
    \vspace{5pt}
    \textbf{Keywords}: Monte Carlo simulations, Log-normal distribution, Poisson distribution

@@

\subsubsection{Details about Model of House Price}
We start with the assumption that house prices, when adjusted for inflation ($A_i$), are normally distributed. A normal distribution is parameterized by its mean ($\mu$) and variance ($\sigma^2$), and its probability density function (pdf) is given by:

>>>>

% 此处填写摘要内容
\begin{abstract}
    The aim of this study is to construct a mathematical model based on Markov chains to predict \
    the total size of claims paid by insurers in the UK (and specifically England) due to fires in \
    the coming year. We split the regions of England into\ 
    \emph{"South West", "South East", "London", "East of England", "East Midlands", "Yorkshire and The Humber", "North West", "West Midlands", "North East"} \ 
    in order to obtain more refined predictions. First, we used house price data as a proxy for the \
    size of the claim per fire, assuming a fixed ratio of damage to the size of the claim per fire. \
    We then fitted the house price data with a log-normal distribution to obtain the distribution of \
    each claim size. Next, we modelled the number of fires using a Poisson distribution with a high \
    probability estimate. Finally, we use Monte Carlo simulations to estimate the size of the annual \
    fire loss. Our model takes into account two key factors, the number of fires and the size of claims \
    per fire, and provides insurers with an effective tool for predicting and managing fire insurance risk. \
    However, there are some assumptions and limitations to our model, such as our assumption of a fixed ratio \
    of losses to claim sizes per fire, which may not be entirely accurate in real life situations. \
    Future research could further improve this model to increase its predictive accuracy and usefulness. \\
    All data is taken from GOV.UK, the official website of the UK government.\\

    All Source code you can found in my \href{https://github.com/JavaZeroo/markov\_project}{Github: https://github.com/JavaZeroo/markov\_project}

    \vspace{5pt}
    \textbf{Keywords}: Monte Carlo simulations, Log-normal distribution, Poisson distribution

    \vspace{5pt}
    \textbf{Word Count}: 2936

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效

@@

\subsubsection{Details about Model of House Price}
We start with the assumption that house prices, when adjusted for inflation ($A_i$), are normally distributed. A normal distribution is parameterized by its mean ($\mu$) and variance ($\sigma^2$), and its probability density function (pdf) is given by\textsuperscript{\cite{lognorm}}:
